\documentclass[12pt,a4paper]{article}
\usepackage{ctex}
\usepackage{emptypage} 
\usepackage{fancyhdr}
\usepackage{amsmath,amsfonts,amssymb,mathtools}
\usepackage{graphicx}
\usepackage{mathptmx}
\usepackage{booktabs}
\usepackage[labelfont=bf]{caption}
\usepackage{indentfirst}
\usepackage{caption}
\usepackage{enumitem}
\usepackage[marginal]{footmisc}
\usepackage{subfigure}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{float}
\newgeometry{left=3cm,top=2.5cm,bottom=2.5cm,right=3cm}
\setmainfont{Times New Roman}
\setCJKmainfont[BoldFont=SimHei,ItalicFont=KaiTi]{SimSun}

\lstset{
	backgroundcolor=\color{green!10!blue!15},
	rulesepcolor= \color{red!40!blue!100},
	breaklines=true,
	breakatwhitespace=false,
	numbers=left, 
	numberstyle= \small,
	keywordstyle= \color{blue},
	commentstyle=\color{gray}, 
	frame=shadowbox
}

\renewcommand{\baselinestretch}{1.5}

\title{\textbf{Review of the development of bionic quadruped robots}}

\author{
\\
\Large{Chao Ma \quad 201300066}
\\[6pt]
{ \large \textit{School of Artificial Intelligence, Nanjing University}}\\[2pt]\large \textit{maple@smail.nju.edu.cn}
}

\date{}
\newcommand{\supercite}[1]{\textsuperscript{\cite{#1}}}

\begin{document}
\maketitle
\setcounter{page}{1}
\textbf{Abstract:} \quad {Bionic robots have always been a very important part of the field of robotics research. Bionic robotics is an important branch of robotics, which mainly studies the construction of a robot by simulating the structure of animals, sensing systems, and computational structures. As we all know, in nature, quadrupeds are a huge branch of the animal kingdom. Each animal has different habits or modes of movement, so there are many of these animals that can be discovered by people to study robots. the point. A quadruped robot is a type of legged robot that is superior to wheeled and tracked robots because it has the potential to explore all terrains like humans and animals. Today, mobile robots represented by quadruped robots have a wide range of applications in various fields such as space exploration, military applications, and industrial applications. This paper will give a brief overview and review of the development of quadruped robots over the years, and make a brief prospect of the future development of bionic robots.} \\

\textbf{Key words:}\quad {Quadruped robot;Bionic robot;Footed robot;Gait}
\\[60pt]
\end{document}